\documentclass{article}
\usepackage{courier} 
\usepackage{textcomp} % for symbols like tilde and backslash
\newcommand{\textapprox}{\raisebox{0.5ex}{\texttildelow}}
\setlength\parindent{0pt}

\begin{document}
To begin I downloaded a single chromosome worth of genomes from GnomAD v.r2.0.2.
To shorten the data I used a filter on location script using vcfHacks to get only immune-related genes from chr21 (since this was the smallest vcf to download).


\medskip \texttt{\$ perl \texttildelow/vcfhacks/filterVcfOnLocation.pl \textbackslash \\
-i \texttildelow/gnomad/gnomad.genomes.r2.0.2.sites.chr21.vcf.gz \textbackslash \\
-o \texttildelow/gnomad/Immune.gnomad.chr21.vcf.gz \textbackslash \\
-b Immune\_list\_bed.txt
\medskip}

I then shortened the coloumn to only the first ten or so since we only need a fraction of the information such as allele count and frequency, but not most of the other data.

\medskip \texttt{used vim to remove headers: v130Gd esc :wq \\
\$ awk -F";InbreedingCoeff" 'NF\{print \$1\}' in.tsv -> out.tsv \\
\$ less out.tsv | head -2 \\
}

\medskip \texttt{==>\\
CHROM   POS ID  REF ALT QUAL    FILTER  INFO\\
21  34621214    .   C   G   569.40  PASS    AC=2;AF=6.45536e-05;AN=30982;\\
BaseQRankSum=1.19000e+00;ClippingRankSum=2.58000e+00;DP=666446;\\FS=1.50180e+01\\
\medskip}

In the first instance the file is tsv. I prefer to work with csv as a base. 
To convert tabs to comma is not the most eliquent process on MacOS (that I have found yet).
The command is simple but has to be envoked manually. 
The tab character (after ``s/'' in the following command) must be removed and printed to the command line using ``ctrl+v'' then ``tab''.

\medskip \texttt{\$ sed 's/ /,/g' input.tsv > output.csv}
\medskip

The IFNO section aslo contains some of the inforation that we will need to use as individual columns. 
However, they are separated by semi colons. 
To make comma separated we use the same sed replace method. 
Both of these steps can be piped together for the whole genome implimentation. 

\medskip \texttt{\$ sed 's/;/,/g' output.csv > finalOutput.csv}
\medskip

We want to give each observable a unique header. This can be done using R.
In R we will load the data.

%\medskip \texttt{\$ install.packages("tidyverse")\\
%\$ library(readr)\\
%\$ read\_tsv("\texttildelow/gnomad/immune.short.tsv")\\
%}

\medskip \texttt{\$ 
immune <- read.csv("~/gnomad/immune.csv", header=FALSE)\\
\$ colnames(immune) <- c(\\
"CHRO","POS","ID", "REF", "ALT", "QUAL", "FILT",\\
"AC", "AF", "AN", "BaseQRankSum", "ClippingRankSum", "DP", "FS"\\
}



\end{document}
